\textit{Supplemental materials for:} High-order cognition is supported by information-rich but compressible brain activity patterns

### 2023-03-15 paper/main.tex
finished creating and documenting remaining figures

\newcommand{\synthThirds}{S1}
\newcommand{\accuracyNetworks}{S2}
\newcommand{\componentsNetworks}{S3}
\newcommand{\componentBrains}{S4}
\newcommand{\topTerms}{S5}

@@

\caption{\textbf{Summary of functions associated with top-weighted components
by condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and several core cognitive function classifications is
displayed in the lower right of the figure. Table~\topics~provides a list of
each topic's top-weighted terms, along with each topic's manually labeled
cognitive classification. A full list of the topics most highly associated with
each component may be found in Figure~\topTerms. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\componentBrains) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition components, by
component.} Each sub-panels network plot summarizes the pattern of correlations
between the $n$\textsuperscript{th} top-weighted principal components
(sub-panel) for each experimental condition (gray-outlined dots). The line
thicknesses are proportional to the correlation values (correlation
coefficients are noted in the heatmaps in Panel C).}

>>>>

\newcommand{\synthThirds}{S1}
\newcommand{\accuracyNetworks}{S2}
\newcommand{\componentsNetworks}{S3}
\newcommand{\componentBrains}{S4}
\newcommand{\topTerms}{S5}
\newcommand{\neurosynthFull}{S6}

@@

\caption{\textbf{Summary of functions associated with top-weighted components
by condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and several core cognitive function classifications is
displayed in the lower right of the figure. Table~\topics~provides a list of
each topic's top-weighted terms, along with each topic's manually labeled
cognitive classification. A full list of the topics most highly associated with
each component may be found in Figure~\topTerms. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\componentBrains) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition components, by
component.} Each sub-panels network plot summarizes the pattern of correlations
between the $n$\textsuperscript{th} top-weighted principal components
(sub-panel) for each experimental condition (gray-outlined dots). The line
thicknesses are proportional to the correlation values (correlation
coefficients are noted in the heatmaps in Panel C). Also see
Fig.~\neurosynthFull~for additional information.}

### 2023-03-15 paper/supplement.tex
finished creating and documenting remaining figures

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{supertabular}

\linenumbers

\newcommand{\synth}{1}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{supertabular}{rlllllllllll}

@@

\end{supertabular}

@@

\label{tab:topics}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/top_terms_by_component}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/topic_contrasts}

\caption{\textbf{Fill this in...}}

@@

>>>>

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{xtab}

%\linenumbers

\newcommand{\synth}{1}
\newcommand{\neurosynth}{5}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{xtabular}{rlllllllllll}

@@

 \label{tab:topics}}
\end{xtabular}

@@

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/variance_explained}

\caption{\textbf{Cumulative variance explained by component, condition, and part.} 
Each panel displays the cumulative variance explained in the neuroimaging data as a function of the number of principal components.
Colors denote experimental conditions.  The left panel displays results for all data, and the right panels display results separated
by story segment (Q1: first quarter; Q2: second quarter; Q3: third quarter; Q4: fourth quarter).}

\label{fig:var-explained}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/top_terms_by_component}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/component_brain_maps}

\caption{\textbf{Brain maps by component and condition.} For the top five
highest-weighted principal components (rows), from each experimental condition
(columns), the components' brain maps are projected onto four views: left
sagittal, axial, right sagittal, and coronal.  The color scale is the same for all panels and matches the coloring in Fig.~\neurosynth C.}

\label{fig:components}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/topic_contrasts}

\caption{\textbf{Comparisons between per-component topic correlations across conditions.}  Each sub-panel displays a scatterplot comparing the per-topic correlations for two or more experimental conditions.
Each dot donotes the correlations for a single topic (indicated by the legend on the right).  The topics are colored according to the ranked order of the correlations
between the topic's brain maps and the brain map for the first principal component in the intact condition.  \textbf{A. Comparisons between correlations for each pair of experimental conditions.}  The
conditions being compared are marked on the $x$ and $y$ axes.  Each sub-panel (column) reflects the correlations for one principal component.  \textbf{B. Comparisons between \textit{differences} in correlations for pairs of experimental conditions.}
In these sub-panels, the $x$ and $y$ coordinates reflect differences in correlations for the indicated experimental conditions, for the given component (column).
All panels: the across-topic correlations reported in each panel are between each topic's $x$ and $y$ coordinates.}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/components_neurosynth_full}

\caption{\textbf{Functions associated with top-weighted components by
condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and cognitive function classifications is displayed in
the lower right of the figure. Table~S1 provides a list of each topic's
top-weighted terms, along with each topic's manually labeled cognitive
classification. A full list of the topics most highly associated with each
component may be found in Figure~\ref{fig:top-terms}. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\componentBrains) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition topic weights, by
component.} Each sub-panels network plot summarizes the pattern of correlations
between the topic correlations from each of the $n$\textsuperscript{th} top-weighted principal components
(sub-panel), for each experimental condition (gray-outlined dots). The line
thicknesses are proportional to the correlation values (correlation
coefficients are noted in the heatmaps in Panel C).}

\label{fig:neurosynth-full}
\end{figure}
